---
title: "viz_part_01"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## lets import data'

```{r}
library(tidyverse)
library(ggridges)

```




```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_df
```


Let's make a scatterplot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
geom_point() 

```


Let's make same scatterplot, but different

```{r}
weather_df %>%
  drop_na() %>%
  filter(name == "CentralPark_NY") %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

more of the same but not

```{r}
weather_scatterplot = 
  weather_df %>%
  drop_na() %>%
    ggplot(aes(x = tmin, y = tmax)) 

weather_scatterplot + 
  geom_point()

```

##make it fancy

#the color applies to all the geom stuffz
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() +
  geom_smooth()


```

#this colr only applies to geom_point

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth()
```


```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .3) +
  geom_smooth(se = FALSE)

```

separate panels

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .3) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

`tmax` vs `tmin` is boring, lets spice it up some 

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = .3) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~name) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```


##some quick stuff

weather_df %>% 
  mutate(CONVERT TO FAHENHEIT)



if you have a LOT of data

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex()
```


##univariate plots ... 

Histograms, density, boxplots, violins, etc

```{r}
weather_df %>% 
  ggplot(aes(x = tmax, fill = name)) +
  geom_histogram() +
  facet_grid(. ~name)
```

more options


```{r}
weather_df %>% 
  ggplot(aes(x = tmax, fill = name)) +
  geom_density(alpha = .3)
```

^can do color = name as well for only lines 


```{r}
weather_df %>% 
  ggplot(aes(x = name, y=tmax, fill = name)) +
  geom_boxplot()
```

```{r}
weather_df %>% 
  ggplot(aes(x = name, y=tmax, fill = name)) +
  geom_violin()
```

OR


```{r}
weather_df %>% 
  ggplot(aes(x = tmax, y = name)) +
  geom_density_ridges()
```











